Report on Lab 1 \& Lab 2 in EDA282, Parallel Computer Organization and Design

### 2014-10-11 lab/report/include/lab2.tex
listing

\section{Lab 2}
\label{sec:lab2}
\todo[inline]{Introduction, one paragraph}

@@

\subsection{Task 2}
\todo[inline]{Explain our parallel version}

@@

\subsection{Task 4}
\todo[inline]{
Outline a strategy to modify the MESI protocol to support the O state.
Analyze the MESI\_SMPCache.cpp source to understand how the MESI protocol is currently modeled.
Discuss changes that need to be made to the readLine, writeLine, readRemoteAction, and writeRemoteAction functions. Show the necessary changes in pseudocode. Should the code that tracks cache access statistics be modified? If so, how?}

>>>>

\section{Lab 2}
\label{sec:lab2}
OpenMP (Open \textbf Multi-\textbf Processing)
\todo[inline]{Introduction, one paragraph}

@@

The program reads a matrix on the form $n \times n, n \in [4,8,25,100,200]$ containing data points from a file. To make the program simpler and avoid special cases a padding is added to the matrix changing its dimensions to $(n+2) \times (n+2)$. Then every other data point, here by called red dots, is looped through. For every red dot an average of itself and its neighbors to the west, south, north, and east is calculated and written as the dots new value. For all the other data points, called black dots, the same thing is performed. The difference of the dots new and old value is added together and the process is repeated until this accumulated difference of averages is smaller than 0.01. After the program finishes its execution the matrix have converged to an average of all red and black dots.

\subsection{Task 2}
\todo[inline]{Explain our parallel version}
In listing~\ref{lst:solve} a parallelized version of the function \texttt{void Solve(double **A)} are shown. The parallelization have been done using directives from the OpenMP API. Only this function is shown as the other parts of the program for reading the input file and printing to the console is not included in the performance analysis. The approach taken for making the function execute in parallel is to distribute all the lines of the matrix evenly between all threads.

\lstinputlisting[caption={\textit{Parallel version of original} \texttt{void Solve(double **A)}}, label={lst:solve}]{include/solve.c}

@@

\subsection{Task 4}
\todo[inline]{
Outline a strategy to modify the MESI protocol to support the O state.
Analyze the MESI\_SMPCache.cpp source to understand how the MESI protocol is currently modeled.
Discuss changes that need to be made to the readLine, writeLine, readRemoteAction, and writeRemoteAction functions. Show the necessary changes in pseducode. Should the code that tracks cache access statistics be modified? If so, how?}

### 2014-10-11 lab/report/main.tex
hrj
added intro
listing

\documentclass[a4paper]{report}

\include{packages}

%MACROS---
\newcommand{\reffig}[1]{Fig. \ref{#1}}

\begin{document}
\section{test}
heeeej!!! :)
\end{document}

>>>>

\documentclass[a4paper]{article}

\include{packages}
\usepackage{color}
%MACROS---
\newcommand{\reffig}[1]{Fig. \ref{#1}}

\title{Report on Lab 1 \& Lab 2 in EDA282, Parallel Computer Organization and Design}
\date{October 2014}
\author{Dan Larsson, Jonas Hemlin
\\Master Program of Embedded Electronic Systems Design\\
Chalmers University of Technology, Gothenburg, Sweden\\
Email: \{larsdan, jhemlin\}@student.chalmers.se}

\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}

\lstset{ 
	language=C,
	backgroundcolor=\color{white},
	basicstyle=\tiny,        % the size of the fonts that are used for the code
	breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
	breaklines=true,                 % sets automatic line breaking
	captionpos=t,                    % sets the caption-position to bottom
	commentstyle=\color{mygreen},    % comment style
	deletekeywords={},
	morekeywords={pragma,schedule,reduction,omp,single,private,shared, parallel},            
	extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
	frame=single,                    % adds a frame around the code
	keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
	keywordstyle=\color{blue},       % keyword style
	numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
	numbersep=5pt,                   % how far the line-numbers are from the code
	numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
	rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
	showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
	showstringspaces=false,          % underline spaces within strings only
	showtabs=false,                  % show tabs within strings adding particular underscores
	stepnumber=2,                    % the step between two line-numbers. If it's 1, each line will be numbered
	stringstyle=\color{mymauve},     % string literal style
	tabsize=2                       % sets default tabsize to 2 spaces                   % show the filename of files included with \lstinputlisting; also try caption instead of title
}

\begin{document}
\maketitle

\input{include/lab1}
\input{include/lab2}
\input{include/discussion}
\end{document}
